---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

This is some code (it is less than an R package) for estimating a distribution of a latent variable using Kotlarski's Lemma; in particular, implementing the results in Li and Vuong (1998).

The setup is one where one is interested in the distribution of some latent variable $X$.  One observes two measured with error versions of $X$; call these $X_1$ and $X_2$, and they are given by

\begin{align*}
  X_1 &= X + \epsilon_1 \\
  X_2 &= X + \epsilon_2
\end{align*}

and under the condition that $X$, $\epsilon_1$, and $\epsilon_2$ are mutually independent.  The provided code (two files: `kotlarski.R` and `tuning_parameters.R`) will estimate the pdf of $X$ in this case.

To get things working, you to follow the following steps

- Execute the code in `tuning_parameters.R` -- you should set the values of the tuning parameters to be whatever you want them to be (some preliminary values are set there that work in the example below, but are not guaranteed to work across applications)
- Using your data that includes exactly two measurements of the latent variable, save these in variables called `X1` and `X2`
- Once you have completed these two steps, just run `cf2dens(kotlarski, tgrid, xgrid)` -- `kotlarski` is the name of the function that does most of the work here, `tgrid` and `xgrid` are set in `tuning_parameters.R`


```{r}
#-----------------------------------------------------------------------------
# Some simulations to check that everything works
#-----------------------------------------------------------------------------
```

```{r, echo=FALSE}
# load the code
source("~/Dropbox/kotlarski/R/kotlarski.R")
source("~/Dropbox/kotlarski/R/tuning_parameters.R")
```


```{r, eval=FALSE}
# load the code
source("/path/to/code/kotlarski.R")
source("/path/to/code/tuning_parameters.R")
```


```{r}
n <- 5000
X <- rnorm(n)
e1 <- rnorm(n)
e2 <- rnorm(n)
X1 <- X + e1
X2 <- X + e2



```